Robust Late Fusion Based on Matrix Factorization

### 2016-09-10 ensemble_clustering.tex
Merge Introduction By Yan. and Complete Related Work

\title{Outlier Rejection for Late Fusion on Visual Recognition}

@@

%% Written by DXY:
%%% We formulate the late score fusion algorithm as ensemble clustering problem, and propose an efficient optimization algorithm, namely Score Fusion via Ensemble Cluster(SFEC). SFEC has capability to remove outliers of label assignments from multiple classifiers using a $\ell_{2,1}$ loss, which improves the performance of late fusion (large scale ability). To the best of our knowledge, this is the first work to connect ensemble clustering with late fusion. Compared to the state-of-the-art fusion algorithm, the SFEC achieves promising improvements on large scale dataset such as UCF101.
\end{abstract}

@@

%背景 多model融合
Image or video data in the real world can be represented in multiple features.
For example, motion features of videos can be extracted by Dense Trajectories~\cite{Wang2011Action}.
Shape features of frames can be represented by Histograms of Oriented Gradients~\cite{dalal2005histograms} and Scale-Invariant Feature Transform~\cite{lowe2004distinctive}, and some complex CNN features for both frames and sequences can be trained by ~\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,Xu_2015_CVPR}.
Each feature contains rich information of real data, which can not capture all views of our data.
A single classifier model will bias on some characteristics of training data based on different features.
It can significantly improve the performance by combining multiple features together and capturing more views on data.

%%A single model results could be inaccurate in vision recogonition, so some researchers study how to fuse multiple models to boost the performance, such as the algorithms proposed in \cite{gehler2009feature,xuiccv2013feature,Rakotomamonjy2008Simplemkl}. Fusion techniques can be grouped into two types which are early fusion and late fusion, early fusion fusion multiple models in the feature level, late fusion merge the result of each classifier.

%% late fusion is a common sigle model -> single feature, 介绍late fusion
Late fusion is a common method to make the combination of different features. Single model is firstly trained on different features using Support Vector Machine(SVM) or other classifiers, and then late fusion methods combine the predicted decision results of each single model to decide the final result.
A popular family of late fusion algorithm is that estimate a learned weight for each single model and then fuse the weighted prediction results by simple summation. Multiple Kernel Learning(MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} based method learn a linear combination to fuse multiple predicted scores, many works optimize the MKL based late fusion method by leading thresholding, specific weights or robust constraint into algorithm, such as \cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
\yanred{The alogrithms proposed in Robust Principal Components Analysis(RPCA) might also be used for late fusion, which are capable to find the anomalous results among multiple classifers~\cite{gaoijcai2016robust}. }
%%这提了Gao，下一段也提了Gao这样好么？

@@

%% 不同的features 会有意见不同的时候，具体 outlier rejection，might [Gao low rank sparse loss, but the nuclear norm
%% scale poorly , expensive single vd(SVDs) present of , the other way of low MF foucs on least square smooth function
%% least square loss is sensitive to outlier
%% it's unclear to extend MF to nonsmooth function .
%% In this paper we proposed a
%%Another issue in late fusion is that some works based on MKL \cite{xuiccv2013feature} poor ability to extend their algorithm to large scale data, the ensemble clustering alogrithm \cite{gaoijcai2016robust}, which could alse used in fusion, use a matrix inversion learding into a high time complexity.
It is ubiquitous that multiple classifers based on different features would have disagreements on some data, which motivates the outlier rejection might solve this problem. There are some researchers have ability to reject the outlier of multiple results, such as \cite{gaoijcai2016robust} use low rank sparse $\ell_{1,2}$ loss and nuclear norm to solve, which are poorly to extend to large scale data due to the expensive cost of Singular Value Decomposition(SVDs) present in the alogrithm. The other research on matrix factorization foucs on least square smooth loss funcion, which is sensitive to outlier and it's unclear to extend matrix factorization to nonsmooth $\ell_{1,2}$ loss.

In this paper, we introduce an efficient matrix factorization based alogrithm for late fuse, named Outlier Rejection for Late Fusion(ORLF).
We utilize the robust $\ell_{1,2}$ nonsmooth objective fuction~(\ref{eq:typical_mc}) to remove the outlier results among different classifiers. We introduce the low rank constraint to maintain the consistency among differernt classifers.
The formulation can be written as bellow:

\begin{align}\label{eq:typical_mc}
  \min_{\bX} ~&~ || \bX - \bL ||_{1,2}   \nonumber \\
  \st        ~&~ \rank(\bX) \leq k  ,
\end{align}
\noindent

L a is observed matrix, represent the label indicator matrix in our vision recoginition case. X is a low rank matrix recovered from L. Rank function measures the rank of a matrix. $|| \bX ||_{1,2} = \sum_{j = 1}^{M} \sqrt{\sum_{i=1}^{N} \bX_{ij}} = \sum_{j=1}^{M} || \bX_{.j} ||_2$, where $\bX \in \dsR^{N \times M}$.
Problem~(\ref{eq:typical_mc}) is NP-hard due to the presence of the low rank constraint. For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as bellow:
\begin{align}\label{eq:mf_l21}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
\end{align}
\noindent
Most existing matrix factorization optimization methods only consider smooth loss functions, but the $\ell_{1,2}$ loss in \ref{eq:mf_l21} is nonsmooth. In our proposed method(ORLF), we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently.

Our main contribution can be summarized as below:
\begin{itemize}
  \item We propose an efficient late fusion algorithm based on matrix factorization to do outlier rejection.
  \item We extend matrix factorization alogrithm to handle $\ell_{1,2}$ norm function.
  \item Out proposed method empirically shows significantly improvement than other late fusion algorithms.
\end{itemize}

@@

\iffalse
The key aim of matrix completion based methods is to detect the anomalous clusters (bad partitions/assigments) and reconstruct the real assignments,
which is shown in Figure~\ref{fig:anomalous_cluster}.
A typical formulation of matrix completion based methods then can be written as below:
\begin{align}\label{eq:typical_mc}
  \min_{\bX} ~&~ || \bX - \bL ||_2^2   \nonumber \\
  \st        ~&~ \rank(\bX) \leq k  ,
\end{align}
\noindent
where $k$ is a pre-defined rank constraint,
and $\bL \in \dsR^{N \times MK}$.
Here we denote $M$ and $K$ as the number of single clustering assignments and the number of clusters, respectively.
However, the least square loss used in matrix completion is sensitive to the abnormal errors, namely outliers, the not appropriate to capture the anomalous assignments.
The authors in~\cite{gaoijcai2016robust} propose to achieve cluster-wise (column-wise) sparsity of $\bX$ by the $\ell_{1,2}$ norm on $\bX$, which is as follow
\begin{align}\label{eq:mc_l21_gaospaper}
  \min_{\bX} ~&~ || \bL - \bX ||_F^2 + \beta || \bX ||_{1,2}   \nonumber \\
  \st        ~&~ \rank(\bX) \leq k   ,
\end{align}
\noindent
where $|| \bX ||_{1,2} = \sum_{j = 1}^{MK} \sqrt{\sum_{i=1}^{N} \bX_{ij}} = \sum_{j=1}^{MK} || \bX_{.j} ||_2$,
which would make $\bX$ column-wise sparse (beware the direction of the computation of the $\ell_{1,2}$ norm, more details in~\cite{nienips2010efficient}).
Nevertheless, it does not consider the outliers in their loss function.
In fact, the term $|| \bL - \bX ||_F^2$ is sensitive to outliers, and the term $|| \bX ||_{1,2}$ is equivalent to $|| \bX - \bO ||_{1,2}$, which makes $\bX$ fit $\bO$, where $\bO$ is a matrix with all entries as zero.
\fi

\section{Related Work}
%% RPCA robust
%% Matrix F...
%%
\yanred{MF method}

%%RPCA Methods
Recently, \cite{gaoijcai2016robust} have proposed a robust convex ensemble clustering methods, which use the group-norm regularization to remove anomalous columns from cluster assignment matrix. This could also be used in our late fusion application to remove outlier column in the indicator matrix L. \cite{wright2009robust} instroduce a representative Robust PCA algorithm, and \cite{ye2012robust} propose a rank minimization method optimize the RPCA to fuse the predicted confidence scores of multiple models. \yanred{other RPCA and disadvantage}

MKL~\cite{Rakotomamonjy2008Simplemkl} based method is a simple but efficient way to combine different features for late fusion. \cite{vedaldi2009multiple} use MKL to learn an optimal combination of exponential ${\chi}^2$. \cite{gehler2009feature} introduce two boosting approaches inspired by the MKL. \cite{natarajan2012multimodal} combines these diverse features using a two-step strategy employing MKL and late score fusion methods. \cite{lai2015learning} proposed a late fusion method that determines the optimal fusion weights for each sample. \yanred{\cite{xuiccv2013feature} learns the weights, thresholding and smoothing parameters in a joint framework to combine the decision values. Copy from Abs}. \yanred{However, MKL based method...}

@@

\subsection{Problem Formulation}
Suppose there are n testing instances, we denote each instance as a variable $x_i{\in}\dsR^{d}(1{\leq}i{\leq}n)$. Assuming we have already training m classifiers, $f_1(x), f_2(x), ... f_m(x)$, per classifier will predict a score vector $s_{ij}, 1{\leq}i{\leq}n, 1{\leq}j{\leq}m $，represent the result of j-th classifier on i-th testing instance. Our goal is to fusion these predicted confidence score vectors. Firstly, we transfer these score vectors to a label matrix P, each colums represent the highest value position of each instance. Then using label assigment, we convert multiple P matrixs into a 01 indicator matrix L, see as{\ref{fig:framework}}.
The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, and apply a matrix factorization based approach to optimize the objective function as shown in \ref{eq:mf_l21}. The k of the low rank constraint in (\ref{eq:mf_l21}) is the number of class in recoginition task.

\begin{figure}[h]
\centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
\caption{something}\label{fig:framework}
\end{figure}

@@

\subsection{Final Post Process}
As we recover the low rank matrix X from the label assignment matrix L. Intuitively, there is two possible way to get our final fusion results from X. Although L is a 01 matrix obtain by hard label, we could treat it as a soft score matrix, which the position of highest score represent the most possible label predicted by classifiers. X is an approximation of L, we can simply consider X as a soft score matrix, which fix the outliers from L. Two possible post way to processing X are described as bellow:
\begin{itemize}
  \item Average the score matrixs, each of which is a subset of X, the j-th matrix is from (j*k-k+1)-th colum to (j*k)-th colum of X. Then we got $X^*$, a N*K score matrix. we make the position of the highest value in each rows as the predicted label of the i-th instance.
  \item Seprate X into M matrixs $Y_j$, the i-th colum of $Y_j$ the (j*K+i)-th colum. For each matrix $Y_j$, we obtain a column vector by selecting the index of the highest score in each row. Then we use voting from M index matrix to select the final label.
  \item \yanred{Merge X with original soft score}
\end{itemize}
According to the experiments, the first strategy outperform than the second one, we choose the first one as our final post process of fusion method.

@@

\subsection{Post Strategy Selection}
In this section, we first compare three proposed final post strategy on tree small dataset: PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flowers 17~\cite{nilsback2006visual} and Caltech 101~\cite{Li2006One}. Then we analyse the reason we choose the first strategy as our post process method. \yanred{analysis and details of three dataset}.

\begin{table}[h]\small
\centering
\label{table:strategy}
\begin{tabular}{c|c|c|c}
\hline
Method                       & VOC 2007 &  Flowers 17  & Caltech 101 \\\hline
Strategy 1                   & *  &              & \\\hline
Strategy 2                   & *  &              & \\\hline
Strategy 3                   & *  &              & \\\hline
\hline
\end{tabular}
\caption{Mean Accuracy on Three Strategies}
\end{table}

\yanred{Unwork dataset Record Data}

\begin{table}[h]\small
\centering
\label{table:voc2007}
\begin{tabular}{c|c}
\hline
Method                       & Mean Accuracy     \\\hline
ASF                          & 89.04\%           \\
MKL                          & 85.53\%           \\
RCEC                         & 89.60\%           \\
FWOT                         & 89.85\%           \\
LPBoost                      & 90.54\%           \\\hline
Ours                         & 89.57\%           \\
\hline
\end{tabular}
\caption{VOC2007}
\end{table}

>>>>

\title{Robust Late Fusion Based on Matrix Factorization}

@@

\end{abstract}

@@

%背景 多model融合
Feature extraction, which transforms raw data into numerical features, is a prerequisite for most real world applications.
There are often multiple ways to generate numerical features from raw data.
For example, for image data, one can extract hand-crafted features such as scale-invariant feature transform
(SIFT)~\cite{loweijcv2004distinctive}, Histograms of Gradients (HOG)~\cite{dalalcvpr2005histograms} and trained convolutional neural networks (CNNs) features~\cite{krizhevskynips2012imagenet}.
Text data can be represented by term frequency–inverse document frequency (tf-idf)~\cite{manning2008introduction} and word2vec~\cite{mikoloviclr2013efficient}.
%Videos can be represented by Dense Trajectories~\cite{Wang2011Action}, CNNs~\cite{xucvpr2015discriminative}, \etc.
%\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,xucvpr2015discriminative}
Each category of features tends to capture a specific characteristics of data.
A model trained on an individual feature could be biased and hence obtains an unsatisfactory performance.
Existing works have investigate the performance improvement by combining multiple features in real world applications~\cite{gehler2009feature,ye2012robust,xuiccv2013feature,lai2015learning}.

%背景 多model融合
%Image or video data in the real world can be represented in multiple features.
%For example, motion features of videos can be extracted by Dense Trajectories~\cite{Wang2011Action}.
%Shape features of frames can be represented by Histograms of Oriented Gradients~\cite{dalal2005histograms} and 
%Scale-Invariant Feature Transform~\cite{lowe2004distinctive}, and some complex CNN features for both frames and 
%sequences can be trained by ~\cite{szegedy2015going,chatfield2014return,he2015deep,simonyan2014two,Xu_2015_CVPR}.
%Each feature contains rich information of real data, which can not capture all views of our data.
%A single classifier model will bias on some characteristics of training data based on different features.
%It can significantly improve the performance by combining multiple features together and capturing more views on data.

%% late fusion is a common sigle model -> single feature, 介绍late fusion
Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from each individual feature.
A commonly used method is to learn weights for predictions of each feature and linearly combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
Among these algorithms, multiple kernel learning (MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} is often used to train such a weighted combination.
However, a single feature may produce corrupted predictions on some data, which likely degenerates performance.
To deal with this issue, therefore, some works formulate it as a robust low rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
Nevertheless, nuclear norm minimization applied in these works requires singular value decompositions (SVDs), which would be computationally unaffordable for large matrices.

%% late fusion is a common sigle model -> single feature, 介绍late fusion
%%Late fusion is a common method to make the combination of different features. Single model is firstly trained on different features using Support Vector Machine(SVM) or other classifiers, and then late fusion methods combine the predicted decision results of each single model to decide the final result.
%% A popular family of late fusion algorithm is that estimate a learned weight for each single model and then fuse the weighted prediction results by simple summation. Multiple Kernel Learning(MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} based method learn a linear combination to fuse multiple predicted scores, many works optimize the MKL based late fusion method by leading thresholding, specific weights or robust constraint into algorithm, such as \cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
%% \yanred{The alogrithms proposed in Robust Principal Components Analysis(RPCA) might also be used for late fusion, which are capable to find the anomalous results among multiple classifers~\cite{gaoijcai2016robust}. }
%%这提了Gao，下一段也提了Gao这样好么？

@@

%% 不同的features 会有意见不同的时候，具体 outlier rejection，might [Gao low rank sparse loss, but the nuclear norm
%% scale poorly , expensive single vd(SVDs) present of , the other way of low MF foucs on least square smooth function
%% least square loss is sensitive to outlier
%% it's unclear to extend MF to nonsmooth function .
%% In this paper we proposed a
%%Another issue in late fusion is that some works based on MKL \cite{xuiccv2013feature} poor ability to extend their algorithm to large scale data, the ensemble clustering alogrithm \cite{gaoijcai2016robust}, which could alse used in fusion, use a matrix inversion learding into a high time complexity.
%% It is ubiquitous that multiple classifers based on different features would have disagreements on some data, which motivates the outlier rejection might solve this problem. There are some researchers have ability to reject the outlier of multiple results, such as \cite{gaoijcai2016robust} use low rank sparse $\ell_{1,2}$ loss and nuclear norm to solve, which are poorly to extend to large scale data due to the expensive cost of Singular Value Decomposition(SVDs) present in the alogrithm. The other research on matrix factorization foucs on least square smooth loss funcion, which is sensitive to outlier and it's unclear to extend matrix factorization to nonsmooth $\ell_{1,2}$ loss.

To prevent from the expensive nuclear norm minimization, in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low rank label matrix.
As for outlier detection, as shown in Figure~\ref{fig:framework}, we apply robust $\ell_{1,2}$ loss to remove the outlier columns in the label matrix.
Most existing matrix factorization optimization methods, however, only consider smooth loss functions, rather than the nonsmooth loss.
We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to nonsmooth problems.
The main contributions are summarized as below:
\begin{itemize}
  \item We propose an efficient late fusion algorithm based on matrix factorization.
  \item We extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss.
  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
\end{itemize}

%%In this paper, we introduce an efficient matrix factorization based alogrithm for late fuse, named Outlier Rejection for Late Fusion(ORLF).
%%We utilize the robust $\ell_{1,2}$ nonsmooth objective fuction~(\ref{eq:typical_mc}) to remove the outlier results among different classifiers. We introduce the low rank constraint to maintain the consistency among differernt classifers.
%%The formulation can be written as bellow:

%\begin{align}\label{eq:typical_mc}
%  \min_{\bX} ~&~ || \bX - \bL ||_{1,2}   \nonumber \\
%  \st        ~&~ \rank(\bX) \leq k  ,
%\end{align}
%\noindent

%L a is observed matrix, represent the label indicator matrix in our vision recoginition case. X is a low rank matrix recovered from L. Rank function measures the rank of a matrix. $|| \bX ||_{1,2} = \sum_{j = 1}^{M} \sqrt{\sum_{i=1}^{N} \bX_{ij}} = \sum_{j=1}^{M} || \bX_{.j} ||_2$, where $\bX \in \dsR^{N \times M}$.
%Problem~(\ref{eq:typical_mc}) is NP-hard due to the presence of the low rank constraint. For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as bellow:
%\begin{align}\label{eq:mf_l21}
%  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
%  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
%\end{align}
%\noindent
%Most existing matrix factorization optimization methods only consider smooth loss functions, but the $\ell_{1,2}$ loss in \ref{eq:mf_l21} is nonsmooth. In our proposed method(ORLF), we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently.

%Our main contribution can be summarized as below:
%\begin{itemize}
%  \item We propose an efficient late fusion algorithm based on matrix factorization to do outlier rejection.
%  \item We extend matrix factorization alogrithm to handle $\ell_{1,2}$ norm function.
%  \item Out proposed method empirically shows significantly improvement than other late fusion algorithms.
%\end{itemize}

@@

\section{Related Work}
%% Matrix factorization
%% Fusion Methods
%%

Matrix factorization has attracted increasing attention recently,
and many manifold optimization based algorithms have been proposed by exploiting the manifold geometry.
Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
In~\cite{vandereycken2013lowrank}, the authors propose a low rank geometric conjugate gradient (LRGeomCG) method.
In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low rank matrix completion by exploiting the low rank constraint.
In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm is proposed to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.

MKL based method is a simple but efficient way to combine different features for multi-model fusion,
and many improved algorithms have been proposed by introducing more constraint, boosting methods and other optimization.
In~\cite{vedaldi2009multiple}, the authors use MKL to learn an optimal combination of exponential ${\chi}^2$ kernels capturing a different feature channel. 
In~\cite{gehler2009feature}, boosting approaches are proposed to ensemble different features, which learns the correct weighting of multiple predicted confidence scores from different models.
In~\cite{natarajan2012multimodal}, the authors propose a two-step strategy employing MKL and late score fusion methods to combine diverse features, specifically on event detection tasks.
In~\cite{lai2015learning}, a sample specific late fusion based on graph Laplacian with RankSVM style constraints is proposed,
which learns sample specific fusion weights by diffusing the information from labeled samples to the unlabeled one.
In~\cite{xuiccv2013feature}, a optimization algorithm are proposed to combine diverse decision values, 
which learns the weights, thresholding and smoothing parameters in a joint framework.
However, all these mkl based fusion methods or others only learn weights to combine different basic models, which do not consider the outlier rejection in the fusion process specifically.

@@

\subsection{Problem Formulation}
Suppose there are n testing instances, we denote each instance as a variable $x_i{\in}\dsR^{d}(1{\leq}i{\leq}n)$. Assuming we have already training m classifiers, $f_1(x), f_2(x), ... f_m(x)$, per classifier will predict a score vector $s_{ij}, 1{\leq}i{\leq}n, 1{\leq}j{\leq}m $，represent the result of j-th classifier on i-th testing instance. Our goal is to fusion these predicted confidence score vectors. Firstly, we transfer these score vectors to a label matrix P, each colums represent the highest value position of each instance. Then using label assigment, we convert multiple P matrixs into a 01 indicator matrix L, see as{\ref{fig:framework}}.
The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, and apply a matrix factorization based approach to optimize the objective function as shown bellow:

\begin{align}\label{eq:mf_l21}
    \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
    \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
\end{align}
The k of the low rank constraint in (\ref{eq:mf_l21}) is the number of class in recoginition task.

\begin{figure}[h]
\centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
\caption{Frame Work}
\label{fig:framework}
\end{figure}

@@

\subsection{Final Post Process}
As we recover the low rank matrix X from the label assignment matrix L. Intuitively, there is two possible way to get our final fusion results from X. Although L is a 01 matrix obtain by hard label, we could treat it as a soft score matrix, which the position of highest score represent the most possible label predicted by classifiers. X is an approximation of L, we can simply consider X as a soft score matrix, which fix the outliers from L. Three possible post ways processing X are described as bellow, $X_{*j}$ represents the j-th matrix is from (j*k-k+1)-th colum to (j*k)-th colum of X:
\begin{itemize}
  \item Average the score matrixs $X_{*j}$, which is a subset of X. Then we got $X^*$, a $N\times K$ score matrix. we make the position of the highest value in each rows as the predicted label of the i-th instance.
  \item The same pre-process as the first strategy, but we use voting to predict the final label the i-th instance.
  \item We normalize each subset of X by softmax function and the corresponding confidence score matrix Y by L2 norm. Then we treat each element as a gate to the corresponding one in Y, which effects on Y by production. Finally the indicator of the highest value is selected to be the predicted label as the first strategy.
\end{itemize}
According to the experiments, the first strategy outperforms than the others, we choose the first one as our final post process of fusion method and analyse inner reason during experiment section.

@@

\subsection{Post Strategy Selection}
In this section, we first compare three proposed final post strategy on tree small dataset: PASCAL VOC 2007~\cite{pascal-voc-2007}, Oxford Flowers 17~\cite{nilsback2006visual} and Caltech 101~\cite{Li2006One}. PASCAL VOC 2007 contrains 6146 images classified into 20 classes, after filtering the multi-label data. Oxford Flowers 17 dataset havs 17 flower categories with 80 images for each class. Caltech 101 contains a total of 9,146 images, split between 101 distinct object categories and a background category.

Experiment results show that the first strategy outperforms than the others in most cases and never performe under the others. \yanred{Lack Analysis}

\begin{table}[h]\small
\centering
\label{table:strategy}
\begin{tabular}{c|c|c|c}
\hline
Method                       & VOC 2007 &  Flowers 17  & Caltech 101 \\\hline
Strategy 1                   & 89.56\%  &  96.76\%     &    -        \\\hline
Strategy 2                   & 89.26\%  &  96.61\%     &    -        \\\hline
Strategy 3                   & 89.16\%  &  96.75\%     &    -        \\\hline
\hline
\end{tabular}
\caption{Mean Accuracy on Three Strategies}
\end{table}

\subsection{\yanred{Unwork dataset Record Data}}

\yanred{On PASCAL VOC 2007 and Oxford Flowers 17 Datasets.}

\begin{table}[h]\small
\centering
\label{table:voc2007}
\begin{tabular}{c|c}
\hline
Method                       & Mean Accuracy     \\\hline
ASF                          & 89.04\%           \\
MKL                          & 85.53\%           \\
RCEC                         & 89.60\%           \\
FWOT                         & 89.85\%           \\
LPBoost                      & 90.54\%           \\\hline
Ours                         & 89.57\%           \\
\hline
\end{tabular}
\caption{VOC 2007}
\end{table}
